### 2024-04-01 tesis_Ashish/Chapter4/chapter4.tex
update 28 Mar
update 1 April

Figure \ref{fig:fitquality} displays the collision rates for a specific particle bunch as one beam is moved across another, with all necessary corrections applied. $\chi^2/ndof$ for vdM and imaging scans has an average value of 0.4514 where the Poly2G fit model converges for all BCIDs. Peak value and beam overlap $\Sigma_x$ and $\Sigma_y$ along X and Y are extracted from fit to calculate $\sigma_{vis}$. %The $\sigma_{vis}$ per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig. \ref{fig:sigmaperscan}.
The $\sigma_{vis}$ value obtained by averaging all scans for the final module veto list is 960.54 $\pm$ 0.85(stat.) mb.

@@

@@

\item Stability: Systematic uncertainties can be introduced due to time-dependent changes in detector performance and environmental conditions. These changes can be influenced by various factors, including detector aging, radiation damage, and fluctuations in noise. A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig. \ref{fig:stabprof_7098} depicting slight instabilities in PCC luminosity over time.
%Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
Detector aging can result in time-dependent changes in the detector's performance. For example, as the detector ages or sustains radiation damage, its efficiency may decrease, leading to a reduction in the number of detected events for a given luminosity. %This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
The noise level in the detector can also fluctuate over time due to changes in the experimental conditions. Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity. Conversely, high noise levels can also mask genuine events, leading to an underestimate of the luminosity. %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
The standard deviation of ratio of luminosity from best and second best luminometer is used as stability systematic uncertainty as shown in Fig. \ref{fig:stabprof1}. The standard deviation provides a measure of the spread or dispersion of the measurements. If the measurements are stable, the spread will be small, and the standard deviation will be low. Conversely, if there are time-dependent changes in the detector performance or environmental conditions, the measurements will vary more, and the standard deviation will be higher.

>>>>

Figure \ref{fig:fitquality} displays the collision rates for a specific particle bunch as one beam is moved across another, with all necessary corrections applied. $\chi^2/ndof$ for vdM and imaging scans has an average value of 0.4514 where the Poly2G fit model converges for all BCIDs. Peak value and beam overlap $\Sigma_x$ and $\Sigma_y$ along X and Y (shown in Fig. \ref{fig:fitquality_4040}) are extracted from fit to calculate $\sigma_{vis}$. %The $\sigma_{vis}$ per scan is averaged over all BCIDs and its scan to scan variation is shown in Fig. \ref{fig:sigmaperscan}.
The $\sigma_{vis}$ value obtained by averaging all scans for the final module veto list is 960.54 $\pm$ 0.85(stat.) mb.

@@

\begin{figure}[H]
    \centering
    \includegraphics[width=1\textwidth]{ashish_thesis/Poly2G_CapSigma.jpeg}
    \caption[Beam overlap widths]{Beam overlap widths for each vdM and imaging scans.}
    \label{fig:fitquality_4040}
\end{figure}

@@

\item Stability: Systematic uncertainties can be introduced due to time-dependent changes in detector performance and environmental conditions. These changes can be influenced by various factors, including detector aging, radiation damage, and fluctuations in noise. A comparison of PCC luminosity with HFOC luminosity as a function of time is shown in Fig. \ref{fig:stabprof_7098} depicting slight instabilities in PCC luminosity over time.
%Detector Aging and Radiation Damage Detectors used in high-energy physics experiments are subject to aging and radiation damage due to the high-intensity radiation environment they operate in.
Detector aging can result in time-dependent changes in the detector's performance. For example, as the detector ages or sustains radiation damage, its efficiency may decrease, leading to a reduction in the number of detected events for a given luminosity. %This effect is typically modeled and accounted for in the data analysis, but any inaccuracies in the modeling can introduce a systematic uncertainty.
The noise level in the detector can also fluctuate over time due to changes in the experimental conditions. Noise can lead to spurious signals that can be misinterpreted as genuine events, leading to an overestimate of the luminosity. Conversely, high noise levels can also mask genuine events, leading to an overestimate of the luminosity. %Noise can be suppressed using data analysis techniques, but this is not always perfect, and residual noise can introduce a systematic uncertainty.
The standard deviation of ratio of luminosity from best and second best luminometer is used as stability systematic uncertainty as shown in Fig. \ref{fig:stabprof1}. The standard deviation provides a measure of the spread or dispersion of the measurements. If the measurements are stable, the spread will be small, and the standard deviation will be low. Conversely, if there are time-dependent changes in the detector performance or environmental conditions, the measurements will vary more, and the standard deviation will be higher.
